%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://facumolina.github.io/}{\Large Facundo Molina}} & Email : \href{mailto:facu.molina7@gmail.com}{facu.molina7@gmail.com}\\
  \href{https://facumolina.github.io/}{https://facumolina.github.io/} & Mobile : +54-358-483-8631 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Rio Cuarto}{Argentina}
      {PhD student in Computer Science}{Apr. 2017 -- Present}
    \resumeSubheading
      {University of Rio Cuarto}{Argentina}
      {Master of Science in Computer Science;  GPA: 9.43/10.0}{Feb. 2015 -- Feb. 2017}
    \resumeSubheading
      {University of Rio Cuarto}{Argentina}
      {Bachelor of Science in Computer Science;  GPA: 9.33/10.0}{Feb. 2012 -- Dec. 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SMF Consulting S.L}{Spain}
      {Software Engineer}{Apr 2015 - Feb 2019}
      \resumeItemListStart
        \resumeItem{Openbravo ERP}
          {The Openbravo ERP is a web-based ERP business solution for small and medium-sized companies. Developed different Java modules to extend the platform solutions.}
        \resumeItem{Openbravo Web POS}
          {The Openbravo Web POS is a fully web based POS system based on HTML5 technologies. Developed some customizations to extend the functionality of the POS system.}
        \resumeItem{Dev Environment}
          {Setup development environment with technologies such as Apache Tomcat, Apache Ant and PostgreSQL.}
        \resumeItem{Web Services}
          {Developed Java web services to synchronize data between Openbravo and other systems.}
        \resumeItem{OBot}
          {OBot is a bot designed to help users to perform actions on the Openbravo platform. Designed core functionalities of the bot using the Dialogflow framework.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Rio Cuarto}{Argentina}
      {PhD student and Teaching Assistant}{Apr 2017 - Present}
      \resumeItemListStart
        \resumeItem{Research - Machine Learning for Program Analysis}
          {Research on the application of machine learning techniques to different program analysis tasks. Implemented genetic algorithms to explore search spaces composed of logical formulas. Also using a neural network approach to solve supervised learning problems in order to improve program analysis tasks, in particular to learn models from software behaviours.}
        \resumeItem{Teaching Assistant - Computability and Complexity}
          {Course of the 5th year in the Computer Science degree. Involved in creating assignments, exams.}
         \resumeItem{Teaching Assistant - Distributed and Outsourced Software Engineering}
          {Course of the 3th year in the Computer Science degree. Lead the construction of a software system developed by the students during the course.}
      \resumeItemListEnd

	\resumeSubheading
      {Gateway Commercial Finance}{USA}
      {Freelance Software Engineer}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem{ChatBot Development}
          {Designed and developed a Dialogflow based chat bot to interact with customers in a financial domain. }
        \resumeItem{DevOps}
          {Mantainance of a Ruby based website in an AWS environment (using Route 53, S3, Amazon SES, etc.)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Current Research Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Data Structure Object Classification}
      {Using Keras Neural Networks to learn to classify valid and invalid objects in Java Data Structures.}
    \resumeSubItem{Goal Conflict Identification}
      {A Java Genetic Algorithm for Goal Conflict Identification during the Specification phase in the Requirements Engineering process.}
    \resumeSubItem{Learning Symbolic Invariants}
      {Improve Symbolic Execution in the Java Pathfinder system by learning Symbolic Invariants using Neural Networks.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
