%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{article} % Default font size and paper size

\usepackage[utf8]{inputenc}

\usepackage{amsfonts}
\usepackage{longtable}
\usepackage{array}
\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titleformat{\subsection}{\large\scshape\raggedright}{}{1em}{\underline}[] % Text formatting of subsections
\titlespacing{\section}{0pt}{3pt}{5pt} % Spacing around sections
\titlespacing{\subsection}{0pt}{10pt}{2pt} % Spacing around subsections
\usepackage{graphicx}
\begin{document}

\pagestyle{empty} % Removes page numbering

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

{\raggedleft{\Huge Facundo \textsc{Molina}}} \\
\textit{Assistant Professor} \\
\textsc{Email:} \href{mailto:facundom@ucm.es}{facundom@ucm.es} \\
\textsc{Website:} \href{https://facumolina.github.io}{https://facumolina.github.io} \\

{\raggedleft
\textsc{Research Statement:} my main research interests are in the area of \textbf{Software Testing and Analysis} and the use of \textbf{Artificial Intelligence for Software Engineering (AI4SE)}, with the goal of improving software reliability and quality.} \\

\section{Employment History}

\begin{longtable}{>{\raggedleft\arraybackslash}p{0.10\textwidth} p{0.86\textwidth}}
2025/2026 & \textbf{Assistant Professor} - \textit{Complutense University of Madrid}, Madrid, Spain. \\  
& \textbf{Research}. As an Assistant Professor, I conduct research on software testing and analysis and AI4SE. Currently, I'm the leading research in the following projects: 
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{DoGFuzz:} documentation-guided fuzzing for testing Python libraries. This undergoing project involves the use of Large Language Models (LLMs) -- e.g., \href{https://mistral.ai/news/mistral-large}{Mistral Large}, \href{https://openai.com/index/gpt-4/}{OpenAI's GPT-4} -- to extract input constraints from the code documentation, and then use such constraints to guide a fuzzing process for testing APIs in Python libraries, including 
deep learning libraries
like \href{https://www.tensorflow.org/}{TensorFlow} and \href{https://pytorch.org/}{PyTorch}. 
\item \textit{Metamorphic testing for AI models:} this undergoing project aims at developing techniques for the automated inference of metamorphic relations to test the robustness of AI models with the goal of improving the reliability of AI-based software.
\end{itemize} \\
& Additionally, I collaborate in the following research project:
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{ASCEND:} industry project coordinated by Boeing Aerospace Spain SLU and ANZEN Aerospace Engineering SL, where I work with as a member of a team from the IMDEA Software Institute, my previous institution, implementing formal verification-based techniques for model-based safety analyses.
\end{itemize} \\
& \textbf{Teaching}. Currently, I have teaching duties in the following courses:
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{Programming II} (Programación II): I am responsible of a first-year course focused on Python programming for a Data Science degree. 
\item \textit{Programming Technology II} (Tecnología de Programación II): I assist in the practical classes of
a second-year programming-intensive course for Computer Science degrees. 
\end{itemize} \\

2022/2025 & \textbf{Postdoctoral Researcher} - \textit{IMDEA Software Institute}, Madrid, Spain. \\
& I worked as a postdoctoral researcher on software testing and analysis, which included developing and implementing novel program analysis techniques, and disseminating our research on top tier software engineering venues. During this period, I was the leading researcher in the following projects: 
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{Deep Learning Library Testing:} study of the use of machine learning (ML) classifiers to improve the effectiveness of the testing of deep learning libraries. We use ML classiers for input-validity prediction, which is a key aspect in the testing of deep learning libraries, as they often have complex input constraints. We implemented a \href{https://sites.google.com/view/ml4dllconstraints}{prototype} for testing libraries like \href{https://www.tensorflow.org/}{TensorFlow} and \href{https://pytorch.org/}{PyTorch}. 
\item \textit{State Field Coverage:} we propose a novel metric to assess the quality of test oracles in Java by analyzing the proportion of object states, as statically defined in the corresponding classes, that may be accessed during test execution. A static analysis-based \href{https://zenodo.org/records/17255287}{prototype} is implemented to analyze popular Java libraries, e.g., \href{https://commons.apache.org/}{Apache Commons}. 
\end{itemize} \\
&
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{FixCheck:} patch correctness assessment improvement based on random testing and Large Language Models (LLMs). The goal was to automatically provide tests revealing the incorrectness of a patch. FixCheck, a tool for analyzing Java patches is implemented using Java, Python, Docker and also the \href{https://huggingface.co/}{Hugging Face} and \href{https://ollama.com/}{Ollama} frameworks to support LLMs. FixCheck is available at: \href{https://github.com/facumolina/fixcheck}{https://github.com/facumolina/fixcheck}
\end{itemize} \\ 

& Additionally, I collaborated in the following research projects: 
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{Express:} automated generation of test oracles in the form of class invariants using a simulated annealing evolutionary algorithm. The goal was to infer precise invariants to be used as part of a regression testing process. A \href{https://github.com/JuanmaCopia/express}{prototype} for generating class invariants for Java classes is implemented.
\item \textit{MemoRIA:} automated inference of metamorphic oracles combining grammar-based fuzzing, dynamic analysis and SAT-based analysis. A \href{https://zenodo.org/records/10683011}{prototype} is implemented in Java, using \href{https://randoop.github.io/randoop/}{Randoop} (for dynamic analysis) and \href{https://alloytools.org/}{Alloy} (for SAT-based analysis).
\item \textit{PLI:} symbolic execution for programs that manipulate complex heap-allocated data. A \href{https://github.com/JuanmaCopia/spf-pli}{prototype} is implemented in Java on top of the \href{https://github.com/SymbolicPathFinder/jpf-symbc}{Symbolic PathFinder} engine.

\end{itemize} \\ 

2017/2022 & \textbf{Ph.D. Student} - \textit{FaMaF, University of Córdoba}, Argentina. \\ 
& My PhD was focused on developing techniques for the \textit{automated generation of test oracles} using search-based and learning-based techniques (evolutionary algorithms and neural nets). My advisor was Prof. Nazareno Aguirre and my dissertation is available in the UNC \href{https://rdu.unc.edu.ar/handle/11086/26692}{digital repository}. The main contributions of my thesis are: 
\begin{itemize}
\setlength\itemsep{0.1em}
\item \textit{SpecFuzzer:} automated inference of test oracles in the form of class specifications using grammar-based fuzzing. SpecFuzzer, a \href{https://github.com/facumolina/specfuzzer}{tool} for inferring oracles for Java classes is implemented using Java and Python, and built on top of the \href{https://plse.cs.washington.edu/daikon/}{Daikon} dynamic invariant detector. SpecFuzzer is available at: \href{https://github.com/facumolina/specfuzzer}{https://github.com/facumolina/specfuzzer}.
\item \textit{EvoSpex:} search-based inference of postconditions of Java methods using genetic algorithms. The EvoSpex tool, implemented in Java using the \href{https://homepages.ecs.vuw.ac.nz/~lensenandr/jgap/documentation/}{JGAP} library, aims to produce a specification of the method's current behavior, in the form of postcondition assertions. EvoSpex is available at: \href{https://github.com/facumolina/evospex}{https://github.com/facumolina/evospex}.
\item \textit{NNInvs:} data structure object classification using artificial neural networks. A first \href{https://sites.google.com/site/learninginvariants}{prototype} is implemented using Java and Python, relying on the \href{https://scikit-learn.org/stable/index.html}{scikit-learn} library. A second \href{https://sites.google.com/site/learninginvariants}{prototype} is developed (to be used in the context of symbolic execution) using the \href{https://keras.io/}{Keras} deep learning library.
\end{itemize} \\ 

2014/2022 & \textbf{Teaching Assistant} - \textit{Department of Computer Science Department, University of Río Cuarto}, Argentina. \\ 
& I was a Teaching assistant in several courses of a Computer Science degree, including Computability and Complexity, Distributed and Outsourced Software Engineering, and Introduction to Programming. My teaching duties involved being in charge of practical classes where students had to solve assignments. Before graduating in 2017, I was a Student teaching assistant in courses such as Data Structures and Algorithms, Algorithms Design Techniques, Programming Paradigms and System Design and Analysis where I helped other teacher assistants. \\ 

2015/2019 & \textbf{Software Engineer} - \textit{SMF Consulting S.L}. \\ 
& Java Software Developer providing solutions to different customers based on an ERP platform. During this time I worked with different teams implementing backend solutions in Java (CRUD operations, API definitions, and integrations with other platforms), maintaining a PostgreSQL database, extending and improving a frontend for retail operations using JavaScript, and performing DevOps tasks managing AWS and Vultr servers. \\ & \\

\end{longtable}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{longtable}{>{\raggedleft\arraybackslash}p{0.10\textwidth} p{0.86\textwidth}}
\\
2017/2022 & \textbf{Ph.D., Computer Science} \\
& Dissertation: Techniques based on Learning and Search for Specification Inference. \\
& \textit{Faculty of Mathematics, Astronomy, Physics and Computing - FaMaF} \\ & \textit{University of Córdoba} - Argentina \\ & \\

2012/2017 & \textbf{Computer Science Licenciate} \\
& (5-year + thesis undergraduate program of study) \\
& \textit{Department of Computer Science} - \textit{University of Río Cuarto} - Argentina \\ 
& \textsc{Thesis project:} Automatic Learning of Relational Specifications using Evolutionary Computation. \\ 
& \textsc{Average score:} 9.43 out of 10 \\ & \\

2012 -	& \textbf{B.S. in Computer Science} \\
2014 & \textit{Department of Computer Science} - \textit{University of Río Cuarto} - Argentina \\
& \textsc{Thesis project:} Project in the course of Distributed and Outsourced Software Engineering. \\ 
& \textsc{Average score:} 9.33 out of 10 \\ \\ 

\end{longtable}

\section{Publications}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.10\textwidth} p{0.86\textwidth}}

\textsc{April}  & \textbf{Improving Deep Learning Library Testing with Machine Learning} \\
        2026 & \underline{Facundo Molina}, MM Naziri, Feiran Qin, Alessandra Gorla, Marcelo d'Amorim. \\
        & \textit{To appear in the 7th ACM/IEEE International Conference on Automation of Software Test, AST 2026, Rio de Janeiro, Brazil, April 12 - 18, 2026.} \\ & \\

\textsc{October}  & \textbf{State Field Coverage: A Metric for Oracle Quality} \\
        2025 & \underline{Facundo Molina}, Nazareno Aguirre and Alessandra Gorla. \\
        & \textit{40th IEEE/ACM International Conference on Automated Software Engineering, ASE 2025, Seoul, Republic of Korea, November 16 - 20, 2025.} \\ & \\

\textsc{July}  & \textbf{Search-based Inference of Class Invariants} \\
        2025 & Juan Manuel Copia, \underline{Facundo Molina}, Alessandra Gorla, Nazareno Aguirre, Pablo Ponzio. \\
        & \textit{Proceedings of the Genetic and Evolutionary Computation Conference Companion, GECCO 2025, Málaga, Spain, July 14 - 18, 2025.} \href{https://doi.org/10.1145/3715107}{[doi]} \\ & \\

\textsc{May}  & \textbf{Test Oracle Automation in the Era of LLMs} \\
        2025 & \underline{Facundo Molina}, Alessandra Gorla and Marcelo d'Amorim. \\
        & \textit{ACM Transactions on Software Engineering and Methodology, Volume 34, Issue 5.} \href{https://doi.org/10.1145/3715107}{[doi]} \\ & \\

\textsc{July}  & \textbf{Abstraction-Aware Inference of Metamorphic Relations} \\
        2024 & Agustín Nolasco, \underline{Facundo Molina}, Renzo Degiovanni, Alessandra Gorla, Diego Garbervetsky, Mike Papadakis, Sebastian Uchitel, Nazareno Aguirre and Marcelo F. Frias. \\
        & \textit{ACM Conference on the Foundations of Software Engineering, FSE 2024, Porto de Galinhas, Brazil, July 15 - 19, 2024.} \href{https://dl.acm.org/doi/10.1145/3643747}{[doi]} \\ & \\

\textsc{May} 2024 & \textbf{Improving Patch Correctness Analysis via Random Testing and Large Language Models} - \underline{Facundo Molina}, Juan Manuel Copia and Alessandra Gorla. \\
        & \textit{17th IEEE International Conference on Software Testing, Verification and Validation, ICST 2024, Toronto, Canada, May 27 - 31, 2024.} \href{https://doi.org/10.1109/ICST60714.2024.00036}{[doi]} \\ & \\

\textsc{October}  & \textbf{Enabling Efficient Assertion Inference} \\
        2023 & Aayush Garg, Renzo Degiovanni, \underline{Facundo Molina}, Maxime Cordy, Nazareno Aguirre, Mike Papadakis, and Yves Le Traon. \\
        & \textit{IEEE 34th International Symposium on Software Reliability Engineering, ISSRE 2023, Florence, Italy, October 9 - 12, 2023.} \href{https://doi.ieeecomputersociety.org/10.1109/ISSRE59848.2023.00039}{[doi]}\\ & \\

\textsc{October}  & \textbf{Precise Lazy Initialization for Programs with Complex Heap Inputs} \\
        2023 & Juan Manuel Copia, \underline{Facundo Molina}, Nazareno Aguirre, Marcelo F. Frias, Alessandra Gorla, and Pablo Ponzio. \\
        & \textit{IEEE 34th International Symposium on Software Reliability Engineering, ISSRE 2023, Florence, Italy, October 9 - 12, 2023.} \href{https://doi.ieeecomputersociety.org/10.1109/ISSRE59848.2023.00080}{[doi]}\\ & \\

\textsc{September} & \textbf{SpecFuzzer: A Tool for Inferring Class Specifications via Grammar-based} \\
        2023 & \textbf{Fuzzing} - \underline{Facundo Molina}, Nazareno Aguirre and Marcelo d'Amorim. \\
        & \textit{IEEE/ACM 38th International Conference on Automated Software Engineering, ASE 2023, Luxembourg, September 11 - 15, 2023.} \href{https://doi.ieeecomputersociety.org/10.1109/ASE56229.2023.00024}{[doi]}\\ & \\

\textsc{July}  & \textbf{EvoSpex: A Search-based Tool for Postcondition Inference} \\
2023 & \underline{Facundo Molina}, Pablo Ponzio, Nazareno Aguirre and Marcelo F. Frias. \\
& \textit{ACM SIGSOFT 32nd International Symposium on Software Testing and Analysis, ISSTA 2023, Seattle, USA, July 17 - 21, 2023.} \href{https://dl.acm.org/doi/abs/10.1145/3597926.3604928}{[doi]} \\ & \\

\textsc{April} & \textbf{Efficient Bounded Exhaustive Input Generation from Program APIs} \\
        2023 & Mariano Politano, Valeria Bengolea, \underline{Facundo Molina}, Marcelo F. Frias, Nazareno Aguirre, and Pablo Ponzio. \\
	& \textit{26th International Conference on Fundamental Approaches to Software Engineering, FASE 2023, Paris, France, April 22 - 27, 2023.} \href{https://doi.org/10.1007/978-3-031-30826-0_6}{[doi]}\\ & \\

\textsc{November} & \textbf{Learning to Prune Infeasible Paths in Generalized Symbolic Execution} \\
        2022& \underline{Facundo Molina}, Pablo Ponzio, Nazareno Aguirre and Marcelo F. Frias.\\
        & \textit{IEEE 33rd International Symposium on Software Reliability Engineering, ISSRE 2022, Charlotte, NC, USA, October 31 - Nov. 3, 2022.} \href{https://doi.org/10.1109/ISSRE55969.2022.00054}{[doi]} \\ & \\

\textsc{May} & \textbf{Fuzzing Class Specifications} \\
	2022 & \underline{Facundo Molina}, Marcelo d'Amorim and Nazareno Aguirre. \\
	& \textit{Proceedings of the 44th ACM/IEEE International Conference on Software Engineering, ICSE 2022, Pittsburgh, USA, May 22-27, 2022.} \href{https://dl.acm.org/doi/abs/10.1145/3510003.3510120}{[doi]} \\ & \\

\textsc{May}  & \textbf{EvoSpex: An Evolutionary Algorithm for Learning Postconditions} \\
2021 & \underline{Facundo Molina}, Pablo Ponzio, Nazareno Aguirre and Marcelo F. Frias. \\
& \textit{Proceedings of the 43rd ACM/IEEE International Conference on Software Engineering, ICSE 2021, Madrid, Spain, May 23-29, 2021.} \href{https://doi.ieeecomputersociety.org/10.1109/ICSE43902.2021.00112}{[doi]} \\ & \\

\textsc{September}  & \textbf{Applying Learning Techniques to Oracle Synthesis} \\
2020 & \underline{Facundo Molina} \\
& \textit{Doctoral Symposium, Proceedings of the 35th IEEE/ACM International Conference on Automated Software Engineering, ASE 2020, Australia, September 21-25, 2020.} \href{https://dl.acm.org/doi/10.1145/3324884.3415287}{[doi]} \\ & \\

\textsc{July 2019}  & \textbf{An Evolutionary Approach to Translating Operational Specifications into Declarative Specifications} - \underline{Facundo Molina}, César Cornejo, Renzo Degiovanni, Germán Regis, Pablo Castro, Nazareno Aguirre and Marcelo Frias. \\
& \textit{Science of Computer Programming, Volume 181, Pages 47-63, 2019.} \href{https://www.sciencedirect.com/science/article/pii/S0167642319300735}{[doi]} \\ & \\

\textsc{May} & \textbf{Training Binary Classifiers as Data Structure Invariants} \\ 
2019 & \underline{Facundo Molina}, Pablo Ponzio, Renzo Degiovanni, Germán Regis, Nazareno Aguirre and Marcelo Frias. \\
& \textit{Proceedings of the 41th International Conference on Software Engineering, ICSE 2019, Montreal, Canada, May 25-31, 2019.} \href{https://doi.ieeecomputersociety.org/10.1109/ICSE.2019.00084}{[doi]} \\ & \\

\textsc{September}  & \textbf{A Genetic Algorithm for Goal-Conflict Identification} \\ 
2018& Renzo Degiovanni, \underline{Facundo Molina}, Germán Regis and Nazareno Aguirre. \\
& \textit{Proceedings of the 33rd ACM/IEEE International Conference on Automated Software Engineering, ASE 2018, Montpellier, France, September 3-7, 2018.} \href{https://doi.org/10.1145/3238147.3238220}{[doi]} \\ & \\

\textsc{May}  & \textbf{From Operational to Declarative Specifications using a Genetic Algorithm} \\ 
2018 & \underline{Facundo Molina}, Renzo Degiovanni, Germán Regis, Pablo Castro, Nazareno Aguirre and Marcelo Frias. \\
& \textit{Proceedings of the 11th International Workshop on Search-Based Software Testing, SBST@ICSE 2018, Gothenburg, Sweden, May 28-29, 2018.} \href{https://dl.acm.org/doi/10.1145/3194718.3194725}{[doi]} \\ & \\

\textsc{November 2018} & \textbf{An Evolutionary Approach to Translate Operational Specifications into Declarative Specifications} - Facundo Molina, César Cornejo, Renzo Degiovanni, Germán Regis, Pablo Castro, Nazareno Aguirre and Marcelo Frias. \\
& \textit{Proceedings of the 19th Brazilian Symposium on Formal Methods SBMF 2016, Natal, Brazil, November 22-25, 2016.} \href{https://doi.org/10.1007/978-3-319-49815-7_9}{[doi]} \\ & \\

\end{longtable}

\section{Public Talks}

\begin{longtable}{>{\raggedleft\arraybackslash}p{0.10\textwidth} p{0.86\textwidth}}

\textsc{October} 2022 & \textbf{State Field Coverage: A Metric for Oracle Quality} - Research track, ASE conference, Seoul, Republic of Korea. \\ & \\

\textsc{July} 2024 & \textbf{Abstraction-aware Inference of Metamorphic Relations} - Research track, FSE conference, Porto de Galinhas, Brazil. \\ & \\

\textsc{May} 2024  & \textbf{Improving Patch Correctness Analysis via Random Testing and Large Language Models} - Research track, ICST conference, Toronto, Canada. \\ & \\

\textsc{October} 2023 & \textbf{Automated Generation of Test Oracles} -Invited speaker at the \textit{Jornadas de Ciencias de la Computación}, JCC 2023, Rosario, Argentina. \\ & \\

\textsc{September} 2023 & \textbf{SpecFuzzer: A Tool for Inferring Class Specifications via Grammar-based Fuzzing} - Tool Demonstrations track, ASE conference, Luxembourg. \\ & \\

\textsc{July} 2023 & \textbf{EvoSpex: A Search-based Tool for Postcondition Inference} - Tool Demonstrations track, ISSTA conference, Seattle, USA. \\ & \\

\textsc{November} 2022 & \textbf{Learning to Prune Infeasible Paths in Generalized Symbolic Execution} - Research track, ISSRE conference, Charlotte, USA. \\ & \\

\textsc{October} 2022 & \textbf{Fuzzing Class Specifications} - Oral communication, Simposio Argentino de Ingeniería de Software ASSE 2022 (virtual), Argentina. \\ & \\

\textsc{May} 2022 & \textbf{Fuzzing Class Specifications} - Research track, ICSE conference, Pittsburgh, USA. \\ & \\

\textsc{March} 2022 & \textbf{EvoSpex: An Evolutionary Algorithm for Learning Postconditions} - Invited talk, Argentine Workshop on Fundamentals for the Automatic Analysis and Construction of Software FACAS 2022, La Falda, Argentina. \\ & \\

\textsc{October} 2021 & \textbf{EvoSpex: An Evolutionary Algorithm for Learning Postconditions} - Oral communication, Simposio Argentino de Ingeniería de Software ASSE 2021 (virtual), Argentina.\\ & \\

\textsc{May} 2021 & \textbf{EvoSpex: An Evolutionary Algorithm for Learning Postconditions} - Research track, ICSE conference (virtual), Madrid, Spain. \\ & \\

\textsc{September} 2020 & \textbf{Applying Learning Techniques to Oracle Synthesis} - Doctoral symposium, ASE conference (virtual), Melbourne, Australia. \\ & \\

\textsc{May} 2019 & \textbf{Training Binary Classifiers as Data Structure Invariants} - Research track, ICSE conference, Montréal, Canada. \\ & \\

\textsc{March} 2019 & \textbf{Learning Hybrid Invariants to Improve Symbolic Execution on Structurally Complex Inputs} - Invited talk, Argentine Workshop on Fundamentals for the Automatic Analysis and Construction of Software FACAS 2021, La Falda, Argentina. \\ & \\

\textsc{September} 2018 & \textbf{A Genetic Algorithm for Goal-Conflict Identification} - Research track, ASE conference, Montpellier, France. \\ & \\

\textsc{November} 2016 & \textbf{An Evolutionary Approach to Translate Operational Specifications into Declarative Specifications} - Research track, Brazilian Symposium on Formal Methods SBMF 2016, Natal, Brazil. \\ & \\

\end{longtable}

\section{Research Prototypes}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.12\textwidth} p{0.84\textwidth}}

\textbf{FixCheck} & FixCheck is a tool for improving patch correctness analyses in Java. It combines static analysis, random testing and LLMs to automatically generate tests that highlight and explain the potential incorrectness of a patch. \\ 
& FixCheck is available at: \href{https://github.com/facumolina/fixcheck}{https://github.com/facumolina/fixcheck} \\ & \\

\textbf{SpecFuzzer} & SpecFuzzer is a tool that automatically infers test oracles in the form of class specifications (postconditions, invariants), and works for Java classes. SpecFuzzer uses a fuzzer as a generator of candidate assertions; a dynamic invariant detector –Daikon– to filter out assertions invalidated by a test suite; and a mutation-based mechanism to cluster and rank assertions, so that similar constraints are grouped and then the stronger prioritized. \\ 
& SpecFuzzer is available at: \href{https://github.com/facumolina/specfuzzer}{https://github.com/facumolina/specfuzzer} \\ & \\


\textbf{EvoSpex} & EvoSpex is a tool that, given a Java method, uses an evolutionary algorithm to produce a specification of the method's current behavior, in the form of postcondition assertions. EvoSpex implements a classic genetic algorithm that searches for a succinct postcondition that accepts the current method behavior, while rejecting any deviation from such behavior. \\ 
& EvoSpex is available at: \href{https://github.com/facumolina/evospex}{https://github.com/facumolina/evospex} \\ & \\

\textbf{PLI} & PLI is an efficient symbolic execution approach for programs that manipulate complex heap-allocated data structures with rich structural constraints. PLI works for Java, and allows preconditions to be specified as standard operational predicates for concrete structures, eliminating the need for additional specifications tailored to symbolic heaps. \\
& PLI is available at: \href{https://github.com/JuanmaCopia/spf-pli}{https://github.com/JuanmaCopia/spf-pli} \\ & \\

\end{longtable}

\section{Research Grants \& Scholarships}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.06\textwidth} p{0.90\textwidth}}

2017 & \textbf{Doctoral Scholarship} \\ 
& \textit{5-year Scholarship granted by Argentina's National Scientific and Technical Research Council (CONICET) to fund doctoral students.} \\ & \\

2016 & \textbf{EVC-CIN Scholarship} \\ 
& \textit{1-year Scolarship granted by the argentinian National Inter University Council (CIN) to encourage undergraduate students to pursue scientific vocations.} \\ & \\

\end{longtable}

\section{Participation in Funded Research Projects}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.20\textwidth} p{0.76\textwidth}}

11/2023-02/2024 & \textbf{ANZEN: Model-based Safety Analysis through Formal Verification.} This project is a collaboration between IMDEA and Anzen Aerospace Engineering, SL to explore the use of formal verification tools in the context of model-based safety analysis. I participated as part of the team from IMDEA Software. \\ & \\

09/2023-10/2025 & \textbf{ESPADA: Efficient and Secure Data Protection Against Digital Attack.} - Project lead by Juan Caballero and Alessandra Gorla, granted by the spanish Ministerio de Ciencia e Innovación, co-funded by European Union ESF, EIE and NextGeneration funds. I participated as a member of the research team. \\ & \\

12/2022-11/2024 & \textbf{PRODIGY: Asegurando la seguridad, escalabilidad y funcionalidad de los sistemas digitales de procedencia.} - Project lead by Juan Caballero y Pedro Moreno-Sánchez, granted by the spanish Ministerio de Ciencia e Innovación, and co-funded by European Union ESF, EIE and NextGeneration funds. I participated as a member of the research team. \\ & \\

\end{longtable}

\section{Honors \& Awards}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.06\textwidth} p{0.90\textwidth}}

\textsc{2020} & \textbf{Latin America PhD Award} - \textit{A research award for PhD students in computing related fields in their 3rd year or beyond at universities in Latin America, and granted by Microsoft Research.} \\ & \\

\textsc{2018} & \textbf{Best Paper Award} - \textit{From Operational to Declarative Specifications using a Genetic Algorithm 11th International Workshop on Search-Based Software Testing, SBST 2018.} \\ & \\

\textsc{2016} & \textbf{Best Paper Award} - \textit{An Evolutionary Approach to Translate Operational Specifications into Declarative Specifications, 19th Brazilian Symposium on Formal Methods, SBMF 2016.} \\ & \\

\textsc{2016} & \textbf{University of Rio Cuarto flag bearer for a 1-year period} - \textit{Traditional honour in educational institutions in Argentina to the three top students in the institution.} \\ & \\
\end{longtable}

%\section{Teaching Background}
%\begin{longtable}{rl}

%\textsc{March 2018} & \textbf{Teaching Assistant} \\
%\textsc{- June 2022} & \textsc{Courses:} Computability and Complexity, Distributed and Outsourced \\
%& Software Engineering, Introduction to Programming. \\
%& \textit{Department of Computer Science - FCEFQyN} \\
%& \textit{University of Río Cuarto} - Argentina \\ & \\

%\textsc{August 2014} & \textbf{Student Teaching Assistant} \\
%\textsc{- June 2017} & \textsc{Courses:} Data Structures and Algorithms, Algorithms Design Techniques, \\
%& Programming Paradigms, and System Design and Analysis. \\
%& \textit{Department of Computer Science - FCEFQyN} \\
%& \textit{University of Río Cuarto} - Argentina \\ & \\

%\end{longtable}

\section{Supervised Students}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.06\textwidth} p{0.90\textwidth}}

2026 & \textbf{Joaquin Heredia} - \textit{Undergraduate student} - University of Río Cuarto, Argentina. \\
& Thesis: Postcondition Inference from API's Documentation. \\
& Joaquin's thesis studies the inference of postconditions from API documentation using Large Language Models.
This is an ongoing project. \\ & \\

2025 & \textbf{Claudio Dosantos} - \textit{Undergraduate student} - University of Río Cuarto, Argentina. \\
& Thesis: Specification-based Regression Testing: Test Assertions vs Contracts. \\
& Claudio's thesis aims to analyze the effectiveness of regression testing when using different kind of oracles, such as unit assertions and contracts. \\ & \\

2024 & \textbf{Ignacio Gonzalez} - \textit{Undergraduate student} - University of Río Cuarto, Argentina. \\
& Thesis: On the Effects of Automated Test Generation for Specification Inference. \\
& Automated test generation tools play a crucial role on dynamic specification inference techniques. Ignacio's work aims at studying how different test generation approaches affects the effectiveness of specification inference techniques. \\ & \\

2023 & \textbf{Agustin Nolasco} - \textit{Undergraduate student} - University of Río Cuarto, Argentina. \\ 
& Thesis: Interring Equivalent Method Sequences for Metamorphic Testing. \\
& Agustin's thesis presents a new technique for the inference of metamorphic oracles, based on runtime analysis, grammar-based fuzzing and SAT solving. \\ & \\

\end{longtable}

\section{Academic Service}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.06\textwidth} p{0.90\textwidth}}

\textsc{2026} & Reviewer for \textit{IEEE Transactions on Software Engineering (TSE)}. Reviewer for \textit{Software Testing, Verification and Reliability (STVR)}. \\ & \\

\textsc{2025} & Reviewer for \textit{ACM Transactions on Software Engineering and Methodology (TOSEM)}. Reviewer for \textit{IEEE Transactions on Software Engineering (TSE)}. Reviewer for \textit{Software Testing, Verification and Reliability (STVR)}.
Program committee member for \textit{International Conference on Internetware (Internetware 2025)}. Artifact Evaluation committee member for \textit{ACM International Conference on the Foundations of Software Engineering (FSE 2025)}.
Tool Demonstrations committee member for \textit{International Conference on Software Engineering (ICSE 2025).}
\\ & \\

\textsc{2024} & Program committee member for \textit{International Conference on AI Foundation Models and Software Engineering (FORGE 2024)}. Reviewer for \textit{IEEE Transactions on Software Engineering (TSE)}.Programm committee member for of the Industry track at \textit{International Conference on Software Maintenance and Evolution (ICSME 2024).} Artifact Evaluation committee member for \textit{International Conference on Software Engineering (ICSE 2024), International Symposium on Software Testing and Analysis (ISSTA 2024).} \\ & \\

\textsc{2023} & Program committee member for \textit{International Working Conference on Source Code Analysis and Manipulation (SCAM 2023)}. Reviewer for \textit{IEEE Transactions on Software Engineering (TSE)}. Artifact Evaluation committee member for \textit{International Symposium on Software Testing and Analysis (ISSTA 2023), Static Analysis Symposium (SAS 2023).} \\ & \\

\textsc{2022} & Student volunteer for \textit{International Conference on Software Engineering (ICSE 2022).} \\ & \\ 

\textsc{2021} & Program committee member for \textit{International Workshop on Test Oracles (TORACLE 2021)}.Student volunteer for \textit{International Conference on Software Engineering (ICSE 2021).} \\ & \\

\textsc{2019} & Student volunteer for \textit{International Conference on Software Engineering (ICSE 2019).} \\ & \\ 

\textsc{2018} & Student volunteer for \textit{International Conference on Automated Software Engineering (ASE 2018).} \\ & \\ 

\textsc{2017} & Student volunteer for \textit{International Conference on Software Engineering (ICSE 2017).} \\ & \\ 

\end{longtable}

\section{Languages}
\begin{tabular}{rl}
\\
\textsc{Spanish:} & Mother tongue\\
\textsc{English:} & Fluent \\ & \\
\end{tabular}

\end{document}
